The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multiphase Forest Inventories

### 2017-08-28 JStatSoft_forestinventory_master-concordance.tex
update Andreas 28.08.2017(2)

\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:%
1 123 1 1 4 1 1 1 4 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Introduction.Rnw:ofs 131:%
1 95 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 227:%
139 34 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Main structure and modules of the Package.Rnw:ofs 262:%
1 77 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 340:%
175 15 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Twophase_Estimators and their Application.Rnw:ofs 356:%
1 126 1 1 2 4 0 1 2 14 1 1 5 7 0 1 2 2 1 1 2 24 0 1 2 4 1 1 2 4 0 1 2 2 1 1 2 1 0 1 5 6 0 1 2 3 1 1 2 8 0 1 2 157 1 1 7 6 0 1 1 26 0 1 2 3 1 1 2 13 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 5 1 1 6 5 0 1 1 8 0 1 2 7 1 1 2 4 0 1 2 1 1 1 6 5 0 1 1 3 0 1 2 1 1 1 2 11 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 887:%
192}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Threephase_Estimators and their Application.Rnw:ofs 888:%
1 119 1 1 2 8 0 1 2 4 1 1 2 1 0 1 1 3 0 1 2 4 1 1 4 1 1 1 6 8 0 1 2 2 1 1 2 27 0 1 2 4 1 1 4 6 0 1 2 2 1 1 2 8 0 1 2 193 1 1 3 2 0 1 1 3 0 1 2 4 1 1 8 11 0 1 3 1 1 1 4 1 1 1 2 12 0 1 2 4 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 7 1 1 7 10 0 1 3 2 1 1 2 12 0 1 2 6 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1407:%
194 10 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Calculation of Confidence Intervals.Rnw:ofs 1418:%
1 46 1 1 2 11 0 1 2 35 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1513:%
206 8 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Special Cases and Scenarios.Rnw:ofs 1522:%
1 21 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1544:%
216 15 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Analysis and Visualization.Rnw:ofs 1560:%
1 20 1 1 4 6 0 1 2 3 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 7 9 0 1 2 2 1 1 8 10 0 1 2 4 1 1 5 7 0 1 2 6 1 1 2 4 0 1 2 2 1 1 2 26 0 1 2 16 1 1 4 1 1 1 2 11 0 1 2 18 1 1 5 7 0 1 2 4 1 1 3 5 0 1 2 10 1 1 2 4 0 1 2 36 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1818:%
233 3 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Acknowledgements.Rnw:ofs 1822:%
1 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1827:%
238 11 1}

>>>>

\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:%
1 123 1 1 4 1 1 1 4 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Introduction.Rnw:ofs 131:%
1 95 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 227:%
139 34 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Main structure and modules of the Package.Rnw:ofs 262:%
1 77 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 340:%
175 15 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Twophase_Estimators and their Application.Rnw:ofs 356:%
1 126 1 1 2 4 0 1 2 14 1 1 5 7 0 1 2 2 1 1 2 24 0 1 2 4 1 1 2 4 0 1 2 2 1 1 2 1 0 1 5 6 0 1 2 3 1 1 2 8 0 1 2 157 1 1 7 6 0 1 1 26 0 1 2 3 1 1 2 13 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 5 1 1 6 5 0 1 1 8 0 1 2 7 1 1 2 4 0 1 2 1 1 1 6 5 0 1 1 3 0 1 2 1 1 1 2 11 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 887:%
192}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Threephase_Estimators and their Application.Rnw:ofs 888:%
1 119 1 1 2 8 0 1 2 4 1 1 2 1 0 1 1 3 0 1 2 4 1 1 4 1 1 1 6 8 0 1 2 2 1 1 2 27 0 1 2 4 1 1 4 6 0 1 2 2 1 1 2 8 0 1 2 193 1 1 3 2 0 1 1 3 0 1 2 4 1 1 8 11 0 1 3 1 1 1 4 1 1 1 2 12 0 1 2 4 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 7 1 1 7 10 0 1 3 2 1 1 2 12 0 1 2 6 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1407:%
194 10 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Calculation of Confidence Intervals.Rnw:ofs 1418:%
1 44 1 1 2 11 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1485:%
206 8 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Special Cases and Scenarios.Rnw:ofs 1494:%
1 16 1 1 8 18 1 1 2 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 2 8 0 1 2 2 1 1 2 8 0 1 2 62 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1639:%
216 15 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Analysis and Visualization.Rnw:ofs 1655:%
1 20 1 1 4 6 0 1 2 3 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 7 9 0 1 2 2 1 1 8 10 0 1 2 4 1 1 5 7 0 1 2 6 1 1 2 4 0 1 2 2 1 1 2 26 0 1 2 16 1 1 4 1 1 1 2 11 0 1 2 18 1 1 5 7 0 1 2 4 1 1 3 5 0 1 2 10 1 1 2 4 0 1 2 36 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1913:%
233 3 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Acknowledgements.Rnw:ofs 1917:%
1 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1922:%
238 11 1}

### 2017-08-28 rnw/Calculation of Confidence Intervals.Rnw
update Andreas 28.08.2017(2)

The estimated variance of a point estimate provides us with a measure of estimation uncertainty. However, its interpretation is rather diffult to use by practitioners. Converting the estimated variance into a 95\% \textit{confidence interval} allows for a much more intuitive and practice-oriented interpretation of the uncertainties associated to a point estimate. In the design-based framework, it denotes that if we would repreatedly conduct the inventory using the same estimation method, estimator and auxiliary information but each time using a new independently and randomly selected sample, 95\% of the calculated confidence intervals will contain the true but unknown quantity. The confidence level $1-\alpha$ (e.g. 95\%) is thus the frequency or proportion of possible confidence intervals that contain the unknown quantity and is therefore often also referred to as \textit{coverage rate}.

Based on the central limit theorem, it can be assumed that under hypothetical repeated sampling, the point estimates will asymptotically follow a normal distribution. \citet{mandallaz2013a} recommended to better base the confidence intervals on the Student's \textit{t} distribution. The confidence intervals for one-phase as well as two-phase and three-phase global and small area point estimates calculated by the package \pkg{forestinventory} are thus defined as \\

@@

where $\hat{Y}$ is the respective point estimate, $\var(\hat{Y})$ is the respective estimated variance, and $1-\alpha$ is the confidence level. Note that in the three-phase case, $p$ is the number of parameters used in the \textit{full} regression model. In case of cluster-sampling, $n_{2,G}$ is the number of terrestrial clusters (a cluster constitutes the sample unit and comprises multiple sample plots).

In the package, the confidence levels for all estimation methods and estimators can be computed by the S3 generic function \code{confint()}, which requires an estimation object created by the \code{onephase()}, \code{twophase()} or \code{threephase()} function, and the confidence level $1-\alpha$ specified by the argument \code{level} (default value of 0.95, i.e. 95\%). The 95\% confidence intervall of the small area estimates by the \textit{extpsynth} estimator (section \ref{sec:twophase_sae}) can for example be applied by:

@@

>>>>

Whereas the estimated variance of a point estimate provides a measure of estimation uncertainty, its interpretation is rather diffult to use by practitioners. Converting the estimated variance into a 95\% \textit{confidence interval} allows for a much more intuitive and practice-oriented interpretation of the uncertainties associated to a point estimate. The correct interpretation of a confidence interval is not that there is a 95\% probability that it contains the true value.  In the design-based context, the true value of the population parameter we are trying to estimate, albeit unknown, is fixed and the sample is randomly generated under the sampling design. Theoretically, if we were to repreatedly conduct the inventory using the same estimation method, estimator and auxiliary information under newly drawn random samples, and then calculate 95\% confidence intervals from each sample, then 95\% of them are expected to contain the true population parameter. The confidence level $1-\alpha$ (e.g. 95\%) is thus the frequency or proportion of possible confidence intervals that contain the unknown  population parameter and is therefore often also referred to as \textit{coverage rate}.

Based on the central limit theorem, it can be assumed that under hypothetical repeated sampling, the point estimates will asymptotically follow a normal distribution. \citet{mandallaz2013a} recommended to better base the confidence intervals on the Student's \textit{t} distribution. The confidence intervals for one-phase as well as two-phase and three-phase global and small area point estimates are thus defined as \\

@@

where $\hat{Y}$ is the point estimate, $\var(\hat{Y})$ is the estimated variance, and $1-\alpha$ is the confidence level. Note that for three-phase sampling, $p$ constitutes the number of parameters used in the \textit{full} regression model. In case of cluster-sampling, $n_{2,G}$ is the number of terrestrial clusters (a cluster constitutes the sample unit and comprises multiple sample plots).

In the package, the confidence intervals for all estimation methods and estimators can be computed by the S3 generic function \code{confint()}, which requires an estimation object created by the \code{onephase()}, \code{twophase()} or \code{threephase()} function. The 95\% confidence intervall of the small area estimates by the \textit{extpsynth} estimator (section \ref{sec:twophase_sae}) can for example be applied by:

@@

%  NOTE:
% - note that the CIs can be used for hypothesis testing, i.e. it can give us an idea wether
%   an estimate is statistically different from a given value
% - 
%
%

### 2017-08-28 rnw/Special Cases and Scenarios.Rnw
update Andreas 09.08.2017(4)
update Andreas 22.08.2017
update Andreas 28.08.2017(2)

\section{Calculation of Confidence Intervals}
\label{sec:confint_calc}

>>>>

\section{Special Cases and Scenarios}
\label{sec:speccas_and_scen}

% include:
% - categorical variables (zberg) and interaction terms (not so clear to everyone)
% - !!! cluster sampling and differences between (p)small and extended (p)small if cluster is not completely inside small area
% - !!! violation of nested sample design + error handling / data adjustments / printed warnings
% - !!! missing factor levels in s2-sample that occur in s1 / s0 sample + error warning
% - [mention that especially in the case of postratification, the g-weight variance is the preferred type because ...]
%

\subsection{Small Area Estimation under Cluster Sampling}

<<echo=FALSE>>=
extpsynth.clust<- twophase(formula = basal ~ stade + couver + melange, data=zberg,
                     phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
                      cluster = "cluster",
                      small_area = list(sa.col = "ismallold", areas = c("1"),
                                        unbiased = TRUE))
@

\begin{small}
\begin{Schunk}
\begin{Sinput}
R> extpsynth.clust<- twophase(formula = basal ~ stade + couver + melange, data=zberg,
+                      phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
+                      cluster = "cluster",
+                      small_area = list(sa.col = "ismallold", areas = c("1"),
+                                        unbiased = TRUE))
Warning message:
At least one terrestrial cluster not entirely included within the small area 1.
Zero mean residual assumption for small area maybe violated.
Check mean_Rc_x_hat_G and consider alternative estimator 'psmall'
\end{Sinput}
\end{Schunk}
\end{small}

\begin{small}
<<>>=
extpsynth.clust$mean_Rc_x_hat_G
@
\end{small}

\begin{small}
<<>>=
extpsmall.clust<- twophase(formula = basal ~ stade + couver + melange, data=zberg,
                     phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
                      cluster = "cluster",
                      small_area = list(sa.col = "ismallold", areas = c("1"),
                                        unbiased = TRUE),
                     psmall = TRUE)
@
\end{small}

\begin{small}
<<>>=
extpsynth.clust$estimation
@
\end{small}

\begin{small}
<<>>=
extpsmall.clust$estimation
@
\end{small}

% --------------------------------------------------------------------- %
\subsection{Nesting Violation in Sample Design}

% explain
% 
% # Checking the nesting of the sample-design:
% # 1) --> each s2-point muss have the complete set of s1-auxvars (s1-info) available
% # 2) --> each s2-point muss have the complete set of s0-auxvars (s0-info) available
% # 3) --> each s1-point muss have the complete set of s0-auxvars (s0-info) available
